Untitled

### 2024-11-08 code/manuscript_altanalysis.Rmd
more figures

```{r}
library(readxl)
library(did2s)
library(did)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
library(ivreg)
library(fixest)
library(sandwich)
library(lmtest)
library("viridis")

@@

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Staff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Staff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  rbind(

@@

@@

did2s(
      data = df.temptemptemp, 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_first - 1)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

@@

>>>>

```{r}
library(readxl)
library(did2s)
library(did)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
library(ivreg)
library(fixest)
library(sandwich)
library(lmtest)
library("viridis")
library(DescTools)

@@

p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))

@@

winsors <- function(x){ Winsorize(x, val = quantile(x, probs = c(0.01, 0.99), na.rm = TRUE))}

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  select(Post, Treat) %>% 
  cbind(
df.temptemp %>% 
  ungroup() %>% 
  select(Qcomp:Staff) %>% 
  summarise_all(winsors)
) %>% 
  group_by(Post, Treat) %>%

  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Staff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  rbind(

@@

## Benjamini Hochberg
```{r}
core.did.estimates %>% 
  arrange(`Pr...t..`) %>% 
  mutate(`Pr...t..` = as.numeric(`Pr...t..`)) %>% 
  cbind(c(1:nrow(core.did.estimates)) / nrow(core.did.estimates) * 0.1) %>% 
  mutate(Row = row_number()) %>% 
  ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/nrow(core.did.estimates) * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise_all(mean.nas)

## Compared to pre-2020 estimates
```{r}

coeffs.did.pre2020 <- c(0,0,0,0)

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx) & Year < 2020) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.pre2020 <- rbind(coeffs.did.pre2020, model$coeftable[1,])

core.did.estimates.pre2020 <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.pre2020[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

core.did.estimates.pre2020 <- core.did.estimates.pre2020
rownames(core.did.estimates) <- NULL

cbind(core.did.estimates, core.did.estimates.pre2020)

@@

## Closures? Mergers?

df.temptemp %>% 
  filter(Closed == 100 & !is.na(Tx)) %>% 
  select(ModernGranteeID, `BHCMIS ID`, Year)

H80CS00003
```

@@

```
## Back of the envelop

asdf <- df.z.temp %>% 
  filter(Year == 2012) %>% 
  filter(Att > 0) %>% 
  group_by(DirectlyTreated) %>% 
  summarise(Counts = n(), Hours = mean.nas(Total.Hours)) %>% 
  cbind(Changes = c(zip.estimates[3,5], zip.estimates[3,2])) %>% 
  summarise(Num = abs(Changes * Counts), Denom = Hours * Counts) %>% 
  colSums()

asdf[1] / asdf[2]
